POMDP comparisons across sigma_m, sigma_g

### 2017-10-08 appendix/appendixB.Rmd
revised appendixB sims

```{r aethetics, include=FALSE}
#library(printr)
knitr::opts_chunk$set(message=FALSE, comment="")
```

@@

```{r}
fits <- examples %>% do(fit_models(., code=gs_code))
fits 
```

@@

```{r}
dir.create(log_dir)

## POMDP solution (slow, >20,000 seconds per loop memory intensive)
system.time(
  alphas <- 
    parallel::mclapply(1:length(models), 
    function(i){
      log_data <- data.frame(model = "gs", 
                             r = meta[i, "r"][[1]], 
                             K = meta[i, "K"][[1]], 
                             sigma_g = meta[i,"sigma_g"][[1]], 
                             sigma_m = meta[i,"sigma_m"][[1]], 
                             noise = "normal")

@@

@@

```{r}
pars <- examples %>% 
  group_by(commonname) %>% 
  summarise(N = max(SSB)) %>% 
  right_join(pars)
```

@@

```{r}
ex <- examples %>%
  mutate(biomass = index(scaled_biomass, states),          
         catch = index(scaled_catch, actions))  %>% 
  left_join(policy_pars) %>% 
  ungroup()

```{r} 
det_f <- function(S_star, i) 
  map_int(pmax(f(states,0) - S_star[[1]],0), ~ which.min(abs(actions - .x)))[i]
msy_f <- function(F_MSY, i) 
  map_int(states, ~ which.min(abs(actions - .x * F_MSY[[1]])))[i]
pgy_f <- function(F_PGY, i) 
  map_int(states, ~ which.min(abs(actions - .x * F_PGY[[1]])))[i]

@@

historical <- ex %>% 
  group_by(commonname) %>% 
  mutate(det =  det_f(S_star, biomass),
         msy =  msy_f(F_MSY, biomass),
         pgy =  pgy_f(F_PGY, biomass)) %>%
  mutate_if(is.integer, rescale, N=N) %>%
  select(year, biomass, catch, det, msy, pgy, commonname)
```

@@

```{r}
historical %>%
select(year, commonname, pgy, msy, det) %>%
gather(model, stock, -year, -commonname) %>%
  ggplot(aes(year, stock, col=model)) + 
  geom_line(data = historical, aes(year, biomass), col="grey", lwd=1) +
  geom_line(data = historical, aes(year, catch), col="black", lwd=1) +
  geom_line(lwd=1) + facet_wrap(~commonname, scales = "free", ncol=1) + theme_bw()  
```

@@

```{r pomdp_sims}
## FIXME obs, action is in index space!
pomdp_sims <- 
  map2_dfr(models, alphas, function(.x, .y){
             hindcast_pomdp(.x$transition, .x$observation, .x$reward, discount, 
                            obs = historical$scaled_biomass, actions = historical$scaled_catch,
                            state_prior = unif_prior,
                            alpha = .y)$df %>% 
              mutate(method = "pomdp") # include a column labeling method
           },
           .id = "scenario") %>% left_join(meta)
```

>>>>

```{r aethetics, include=FALSE}
#library(printr)
knitr::opts_chunk$set(message=FALSE, comment="", cache=TRUE)
```

@@

```{r}
set.seed(123)
fits <- examples %>% do(fit_models(., code=gs_code))
fits 
```

@@

```{r eval=FALSE}
dir.create(log_dir)

## POMDP solution (slow, >20,000 seconds per loop memory intensive)
system.time(
  alphas <- 
    parallel::mclapply(1:length(models), 
    function(i){
      log_data <- data.frame(model = "gs", 
                             r = meta[i, "r"][[1]], 
                             K = meta[i, "K"][[1]], 
                             sigma_g = meta[i,"sigma_g"][[1]], 
                             sigma_m = meta[i,"sigma_m"][[1]], 
                             noise = "normal",
                             commonname = meta[i, "commonname"][[1]])

@@

```{r}
meta <- meta_from_log(data.frame(model="gs"), log_dir) %>%
  mutate(scenario  = as.character(1:length(sigma_m)))
alphas <- alphas_from_log(meta, log_dir)
#models <- models_from_log(meta)
```

@@

```{r}
pars <- examples %>% 
  group_by(commonname) %>% 
  summarise(N = max(SSB)) %>% 
  right_join(meta)
```

@@

```{r}
index <- function(x, grid) map_int(x, ~ which.min(abs(.x - grid)))

ex <- examples %>%
  mutate(biomass = index(scaled_biomass, states),          
         catch = index(scaled_catch, actions))  %>% 
  left_join(policy_pars) %>% 
  ungroup() 
ex
```

```{r} 
det_f <- function(S_star, i) index(pmax(f(states,0) - S_star[[1]],0), actions)[i]
msy_f <- function(F_MSY, i) index(states * F_MSY[[1]], actions)[i]
pgy_f <- function(F_PGY, i) index(states * F_PGY[[1]], actions)[i]

@@

historical <- ex %>% 
  group_by(commonname) %>% 
  mutate(det =  det_f(S_star, biomass),
         msy =  msy_f(F_MSY, biomass),
         pgy =  pgy_f(F_PGY, biomass)) %>%
  select(year, biomass, catch, det, msy, pgy, commonname, N) %>%
  gather(model, stock, -year, -commonname, -N) %>%
  mutate(stock = states[stock] * N) %>% 
  select(-N)
```

@@

```{r}
historical %>%
  ggplot(aes(year, stock, col=model)) +
  geom_line(lwd=1) +
  scale_color_manual(values = c("black", "grey", "#D9661F", "#00B0DA", "#CFDD45")) +
  facet_wrap(~commonname, scales = "free", ncol=1) + theme_bw()  
```

@@

```{r}
  pomdp_sims <- 
  pmap_dfr(list(models, alphas, 1:dim(meta)[[1]]), 
           function(.x, .y, .z){

             who <- ex$commonname == meta[.z,"commonname"]
             df <- ex[who,]

             hindcast_pomdp(.x$transition, .x$observation, .x$reward, discount, 
                            obs = index(df$scaled_biomass, states), 
                            action = index(df$scaled_catch,states),
                            alpha = .y)$df %>% 
              mutate(method = "pomdp") # include a column labeling method
           },
           .id = "scenario") %>% left_join(meta)
```
```{r}
rescale <- function(x) states[x]

pomdp_sims %>% 
  select(time, obs, action, optimal, commonname, sigma_m) %>%
  mutate_at(c("action", "optimal"), rescale) %>%
  ggplot(aes(time, optimal, col=as.character(sigma_m))) + 
  geom_line() + 
  geom_line(aes(time, action), col="black") +
  facet_wrap(~commonname, scales="free") 
```
